\paragraph{Date:} Wednesday, November 29, 2019
\paragraph{To:} HELP Inc.
\paragraph{From:} Charles Stoksik, Colleen Sun, Geoff Harrison, Mariam Alghamdi
\paragraph{Subject:} HELP Inc. Puerto Rico Strategy
\paragraph{Introduction} This memo is designed to give a general overview of a strategy for HELP Inc that could be implemented in Puerto Rico to service the country after Hurricane Maria. Our team of mathematicians came up with this optimal strategy for servicing hospitals for as many days as possible while also servicing the most roads possible. We would love for your company to take our solution into consideration when deciding how to pursue your relief effort.
\paragraph{Solution} Our solution is outlined as follows: We maximize the number of days we can service the hospitals for and then we attempt to find the best base locations for road reconnaissance. Therefore you should know that our solution chooses initial base locations off of prioritizing servicing hospitals over road reconnaissance. This is because we were given no maximum number of days to service hospitals for and given the severity of the damage we may need to continue to supply care packages for years to come. Therefore, in our solution we find areas such that if we placed home bases in these locations then we could service all of the hospitals. Please see Figure \ref{fig:2_3_map} for a visual explanation. From here we were able to narrow down our base choices to the three which would allow for us to do the most road reconnaissance. This gave us a final result, coordinates given in Table \ref{tab:best_config} and illustrated in Figure \ref{fig:2_5_map}.
\paragraph{Specifications} It is important to also know the specifications of our solution. We predict that with three B drones HELP Inc. would be able to service all five hospitals for 1146 days with this given configuration of bases. Our configuration allows for drones to fly between bases to charge and then continue to deliver packages from other bases. Our solution was created under the assumption that drones can only charge at home bases, and not at hospitals. Since our drones can fly between bases we will split the load of packages between the bases unevenly (one base does not necessarily only serve the same one or two hospitals). We outline how to best split your cargo and drone flight schedule in the relevant sections, however here is a brief rundown: We put the relevant packages for hospitals in the closest container so initially we can service the closest hospitals with the closest containers. Hospital B requires more volume for packages in the 1146 days than the size of the shipping containers, so our schedule will change when we run out of packages to service Hospital B in the container. Our other two containers are initially split with container 1 serving Hospitals A and SJ while container 3 services Hospitals J and SP. Note that both of these containers will eventually service Hospital B when the packages run out in container 2. 
\paragraph{Limitations} We recognize that there are a lot of outside factors that could lead to a disruption in our solution. Some potential further considerations would be issues with packing, deterring drone performance, base location restrictions, topographical restrictions. Firstly packing may not go as planned. We do not account for the 3D-configuration of the packages, we simply consider their volume when allocating space. Secondly, drones could lose range over time and they could consumer more power while carrying packages, thus decreasing their instantaneous range. Thirdly, our base locations could be restricted to ports or near highways because of the infrastructure damage. Lastly and similarly, topography could impact our where we can fly and set up bases too. All of these are important notes as is our assumption that weather is perfect throughout the year, and we recommend that HELP Inc. invests in water-proof drones.
\paragraph{Conclusion} To sum up, this report details the ideal locations for HELP Inc.'s bases while serving Puerto Rico during this humanitarian crisis. We predict that with the base locations in Table \ref{tab:best_config}, HELP Inc. can serve the given Hospitals for 1146 days before the need to resupply. We hope you take our report into consideration and we wish HELP Inc. the best of luck.